\centerline{Sudoku}

### 2021-05-26 report/paper.tex
apology for poor english
when were you when lab2 dies?

i was sat at home doing OM when stefan ring

‘lab2 is kill’

‘no’

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{pics/solved.png}
\caption{Press the \texttt{Solve} button to find the soluscion}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{pics/input_check.png}
\caption{Errors if a number is not in $ \left[ 1, 2,3,4,5,6,7,8, 9 \right] $}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{pics/solved.png}
\caption{Press the \texttt{Solve} button to find the solution}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{pics/input_check.png}
\caption{Errors if a number is not in $ \left[ 1, \hdots n \right] $ (where $n$ is the side of the board)}
\end{figure}
